FinalManuscript_DISCS_UG

### 2018-06-24 parts/01_introduction_05scopeandlimitations.tex
Added temporary scope and limitations

In order for your study to be realistic, doable, and still produce a concise answer to your research questions within a particular period of time, this section provides you the opportunity to both cross-out extraneous variables, as well as set those aspects that must be controlled in your study. Some common limitation targets include the target audience for the experiment, the software to be used, portability and reusability of the software, the features it will have, and so on.

>>>>

Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to

\textbf{insert listing here}

Our library for OpenCV will be implmented in the C++ programming language.

\textbf{insert other limitations here}
